The Rockerverse: Packages and Applications for Containerization with R

### 2020-01-31 README.Rmd
fix sticker path
high-res sticker option

Draft for an article of everything related to containers and R, originally based on the blog post http://bit.ly/docker-r.

@@

library("hexSticker")
hexSticker::sticker(here::here("whaleverse.png"), package = "ROCKERVERSE",
        p_family = "finalfrontier",
        p_size = 29, p_y = 1.3,
        s_x = 0.97, s_y = 0.95, s_width = 1,
        h_fill = "#000000", h_color = "#ffffff",
        url = "github.com/nuest/rockerverse-paper",
        u_color = "#ffffff", u_size = 4,
        filename = here::here("rockerverse.png"))

@@

![Rockerverse hex sticker](`r here::here("rockerverse.png")`)

Hex sticker uses the font [Final Frontier Old Style](https://www.fontspace.com/allen-r-walden/final-frontier-old-style) and the [Hubble Ultra-Deep Field](https://en.wikipedia.org/wiki/Hubble_Ultra-Deep_Field) combined with the Docker logo as background.

>>>>

Article about everything related to containers and R, originally based on the blog post http://bit.ly/docker-r and now **available as a preprint on arXiv.org: https://arxiv.org/abs/2001.10641**.

@@

library("hexSticker")
factor <- 1 # for print: 4
hexSticker::sticker(here::here("whaleverse.png"), package = "ROCKERVERSE",
        p_family = "finalfrontier",
        p_size = 29 * factor, p_y = 1.3,
        s_x = 0.97, s_y = 0.95, s_width = 1,
        h_fill = "#000000", h_color = "#ffffff",
        url = "github.com/nuest/rockerverse-paper",
        u_color = "#ffffff", u_size = 4 * factor,
        filename = here::here(ifelse(
          factor == 1,
          "rockerverse.png",
          paste0("rockerverse_", 300 * factor, "dpi.png"))),
        dpi = 300 * factor)

@@

![Rockerverse hex sticker](rockerverse.png)

The hex sticker uses the font [Final Frontier Old Style](https://www.fontspace.com/allen-r-walden/final-frontier-old-style) and the [Hubble Ultra-Deep Field](https://en.wikipedia.org/wiki/Hubble_Ultra-Deep_Field) combined with the Docker logo as background.
